### 2021-05-20 LaTeX-ACM/sections/paper.tex
adding evaluations + small edits here and there

\section{Introductory Remarks}

For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology. New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight. Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets. Such exchanges are key components to blockchain-based economic activity.

@@

While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}. While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms.

@@

\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp; \textit{a.k.a.} smart contract). In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds. The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below). Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time. While they sound ideal, performance is a substantial issue and the main subject of this paper. Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).

@@

\cm is proof of concept code. We try to simplify the design at every step to make it an extensible base class but still functional without any extensions. A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}. As markets are relatively short-lived, orders simply expire when the market call period ends.

@@

%\textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar DApps for the market and  a factory DApp to guide users to the correct address (from the reviewer's comment)}

\cm is designed as a base class that can be extended and customized. We discuss potential modifications here.

@@

When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order. In \cm, tokens are assumed to be divisible. We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices). A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work. Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and countermeasures could take a few blocks to select~\cite{boneh2018verifiable}).

@@

\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived. Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes). Finally, cancellations have a performance impact. Canceled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

@@

@@

@@

% JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.

@@

The final issue is who invokes \texttt{closeMarket()} every other block? There are actually two issues here: the issue of scheduling the function call and the issue of paying for it. For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next we consider the second issue of who pays to close the market.

% = = = = = = = = = = = =Who Pays the Cost for Closing and Reopening the Market?= = = = = = = = = = = = =  %

@@

As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself. However we consider two other scenarios that do not assume miners can automatically find MEV opportunities. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).  Once the time window for submitting orders has past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.

@@

>>>>

\section{Introductory Remarks}
\textblue{add sth about the " traversing data structures with e.g., 100 elements on-chain is not possible." contribution somewhere in the intro or contribution section}
For better or worse, blockchain technologies like Ethereum have dramatically lowered the barrier to entry for developing and deploying financial technology. New tokens have been launched with a few clicks of a user interface, and large investment infrastructures have been developed and deployed with little regulatory oversight. Blockchain exchange services allow order-based trading of digital currencies, tokens, and other digital assets. Such exchanges are key components to blockchain-based economic activity.

@@

While Solidity and its compiled bytecode is like many common programming languages, it also has quirks that require experimentation to best optimize performance (\eg factoring in the gas costs of operations, gas refunds, limits to Solidity's object-oriented design, clearing mappings, \etc). We test five priority queues---the core data structure of the call market---and various options for cleaning up our data once finished with it. The bottom line is that the current benchmark for a \cm-esque design is in the low hundreds of trade executions per block on Ethereum today. This positions \cm as a feasible design for only a narrow set of markets today (low liquidity, small number of traders) which is good news for regulators. However we caution that the technology is likely to improve vastly in the coming years and we demonstrate one avenue for improvement through `roll-ups'~\cite{kalodner2018arbitrum}. While roll-ups use centralized servers and are not fully on-chain, an architecture where these servers only interface with Ethereum and never interface directly with users is still concerning, as it side-steps the regulatory hook that is present in many other server-augmented trading platforms. \textblue{say sth about implementing and testing the full call market on Arbitrum}

@@

\paragraph{On-chain Order Books.} For trades between two blockchain-based assets (\eg a digital asset priced with a cryptocurrency, stablecoin, or second digital asset), order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp). In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds. The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running below). Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time. While they sound ideal, performance is a substantial issue and the main subject of this paper. Since it is an open system, there is no obvious regulatory hook (beyond the blockchain itself).

@@

\cm is proof of concept code. We try to simplify the design at every step to make it an extensible base class but still functional without any extensions. A call market will open for a specified period of time during which it will accept a capped number of orders (\eg 100 orders---parameterized so that all orders can be processed), and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block)\textblue{should we add a reference to the section \textbf{who opens/closes the market?}}. We keep the design simple by not allowing cancellations which require a second transaction and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}. As markets are relatively short-lived, orders simply expire when the market call period ends.

@@

\cm is designed as a base class that can be extended and customized. Here, we discuss potential modifications \textblue{and provide evaluation}.  
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

When executing trades, if the volume of the current best bid does not match the best ask, the larger order is partially filled and the remaining volume is considered against the next best order. In \cm, tokens are assumed to be divisible. We simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices).

\paragraph{Evaluation.} A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach does not always work. Consider the following corner case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and countermeasures could take a few blocks to select~\cite{boneh2018verifiable}).

@@

\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived.

\paragraph{Evaluation.} Support for cancellation opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes \textblue{Should we refer to the new front-running section here???} ). Also, cancellations have a performance impact. Canceled orders can be removed from the underlying data structure or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a self-balancing binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

@@

\paragraph{Evaluation.} \textblue{???}
% = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

\textblue{JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.}

@@

@@

The final issue is who invokes \texttt{closeMarket()} every other block? There are actually two issues here: the issue of scheduling the function call and the issue of paying for it. For scheduling the function call, we can do one of the following: rely on market participants, who are eager to trade, to reopen the market, offer a bounty to reopen the market, or use an external service like Ethereum Alarm Clock (which creates a regulatory hook).\footnote{\url{https://ethereum-alarm-clock-service.readthedocs.io/}} Next, we consider the second issue of who pays to close the market.

\paragraph{Evaluation.} \textblue{???}

@@

As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself. However, we consider two other scenarios that do not assume miners can automatically find MEV opportunities. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).  Once the time window for submitting orders has past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market.

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty.

\paragraph{Evaluation.} The first solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close). The second solution is better, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However, an interested third party (such as the token issuer for a given market) might occasionally bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the DApp can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}) which introduces another regulatory hook.

@@

\paragraph{Evaluation.} \textblue{??}
